Testing gene methylation enrichment analysis approaches using simulated data

### 2023-10-18 figs/GSE158422_simulate.Rmd
progress on simulation

suppressPackageStartupMessages({
  library("stringi")
  library("limma")
  library("missMethyl")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylationEPICanno.ilm10b4.hg19")
  library('org.Hs.eg.db')
  library("tictoc")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("eulerr")
})

@@

@@

num_dm_sets=50
sims=4

groupsizes=c(3,6,12,18)
deltas=c(0.1,0.3,0.5,0.7,1.0)
params <- expand.grid("groupsizes"=groupsizes,"deltas"=deltas)
params

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

suppressPackageStartupMessages({
  library("stringi")
  library("limma")
  library("missMethyl")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylationEPICanno.ilm10b4.hg19")
  library('org.Hs.eg.db')
  library("psych")
  library("mitch")
  library("kableExtra")
})

@@

F1 <- function(x,y) {
  ( 2 * x * y ) / ( x + y )
}

@@

num_dm_sets=50
sims=10

groupsizes=c(3,6,12)
deltas=c(0.1,0.2,0.3,0.5)
params <- expand.grid("groupsizes"=groupsizes,"deltas"=deltas)
params

@@

gres3p <- do.call(rbind,lapply(groupsizes, function (g) { gres2[params$groupsizes==g,"PREC"] }))
colnames(gres3p) <- deltas
rownames(gres3p) <- groupsizes
gres3p

gres3r <- do.call(rbind,lapply(groupsizes, function (g) { gres2[params$groupsizes==g,"REC"] }))
colnames(gres3r) <- deltas
rownames(gres3r) <- groupsizes
gres3r

F1(gres3p,gres3r)

@@

lares3p <- do.call(rbind,lapply(groupsizes, function (g) { lares2[params$groupsizes==g,"PREC"] }))
colnames(lares3p) <- deltas
rownames(lares3p) <- groupsizes
lares3p

lares3r <- do.call(rbind,lapply(groupsizes, function (g) { lares2[params$groupsizes==g,"REC"] }))
colnames(lares3r) <- deltas
rownames(lares3r) <- groupsizes
lares3r

F1(lares3p,lares3r)

@@

lacres3p <- do.call(rbind,lapply(groupsizes, function (g) { lacres2[params$groupsizes==g,"PREC"] }))
colnames(lacres3p) <- deltas
rownames(lacres3p) <- groupsizes
lacres3p

lacres3r <- do.call(rbind,lapply(groupsizes, function (g) { lacres2[params$groupsizes==g,"REC"] }))
colnames(lacres3r) <- deltas
rownames(lacres3r) <- groupsizes
lacres3r

F1(lacres3p,lacres3r)

@@

nlares3p <- do.call(rbind,lapply(groupsizes, function (g) { nlares2[params$groupsizes==g,"PREC"] }))
colnames(nlares3p) <- deltas
rownames(nlares3p) <- groupsizes
nlares3p

nlares3r <- do.call(rbind,lapply(groupsizes, function (g) { nlares2[params$groupsizes==g,"REC"] }))
colnames(nlares3r) <- deltas
rownames(nlares3r) <- groupsizes
nlares3r

F1(nlares3p,nlares3r)

@@

nlacres3p <- do.call(rbind,lapply(groupsizes, function (g) { nlacres2[params$groupsizes==g,"PREC"] }))
colnames(nlacres3p) <- deltas
rownames(nlacres3p) <- groupsizes
nlacres3p

nlacres3r <- do.call(rbind,lapply(groupsizes, function (g) { nlacres2[params$groupsizes==g,"REC"] }))
colnames(nlacres3r) <- deltas
rownames(nlacres3r) <- groupsizes
nlacres3r

F1(nlacres3p,nlacres3r)

@@

alres3p <- do.call(rbind,lapply(groupsizes, function (g) { alres2[params$groupsizes==g,"PREC"] }))
colnames(alres3p) <- deltas
rownames(alres3p) <- groupsizes
alres3p

alres3r <- do.call(rbind,lapply(groupsizes, function (g) { alres2[params$groupsizes==g,"REC"] }))
colnames(alres3r) <- deltas
rownames(alres3r) <- groupsizes
alres3r

F1(alres3p,alres3r)

@@

alcres3p <- do.call(rbind,lapply(groupsizes, function (g) { alcres2[params$groupsizes==g,"PREC"] }))
colnames(alcres3p) <- deltas
rownames(alcres3p) <- groupsizes
alcres3p

alcres3r <- do.call(rbind,lapply(groupsizes, function (g) { alcres2[params$groupsizes==g,"REC"] }))
colnames(alcres3r) <- deltas
rownames(alcres3r) <- groupsizes
alcres3r

F1(alcres3p,alcres3r)

@@

nalres3p <- do.call(rbind,lapply(groupsizes, function (g) { nalres2[params$groupsizes==g,"PREC"] }))
colnames(nalres3p) <- deltas
rownames(nalres3p) <- groupsizes
nalres3p

nalres3r <- do.call(rbind,lapply(groupsizes, function (g) { nalres2[params$groupsizes==g,"REC"] }))
colnames(nalres3r) <- deltas
rownames(nalres3r) <- groupsizes
nalres3r

F1(nalres3p,nalres3r)

@@

nalcres3p <- do.call(rbind,lapply(groupsizes, function (g) { nalcres2[params$groupsizes==g,"PREC"] }))
colnames(nalcres3p) <- deltas
rownames(nalcres3p) <- groupsizes
nalcres3p

nalcres3r <- do.call(rbind,lapply(groupsizes, function (g) { nalcres2[params$groupsizes==g,"REC"] }))
colnames(nalcres3r) <- deltas
rownames(nalcres3r) <- groupsizes
nalcres3r

F1(nalcres3p,nalcres3r)

@@

aares3p <- do.call(rbind,lapply(groupsizes, function (g) { aares2[params$groupsizes==g,"PREC"] }))
colnames(aares3p) <- deltas
rownames(aares3p) <- groupsizes
aares3p

aares3r <- do.call(rbind,lapply(groupsizes, function (g) { aares2[params$groupsizes==g,"REC"] }))
colnames(aares3r) <- deltas
rownames(aares3r) <- groupsizes
aares3r

F1(aares3p,aares3r)

@@

almres3p <- do.call(rbind,lapply(groupsizes, function (g) { almres2[params$groupsizes==g,"PREC"] }))
colnames(almres3p) <- deltas
rownames(almres3p) <- groupsizes
almres3p

almres3r <- do.call(rbind,lapply(groupsizes, function (g) { almres2[params$groupsizes==g,"REC"] }))
colnames(almres3r) <- deltas
rownames(almres3r) <- groupsizes
almres3r

F1(almres3p,almres3r)
